---
title: "GIS_Coursework"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Impact of the Coronavirus Pandemic on Crime
This research aims to better understand the impacts of the coronavirus-related social restriction on crime. 

# Part 1: Loading data of COVID-19 
It is simple to load CSV file by R
```{r}
# loading the CSV file of covid-19 
Covid_19_cases<- read.csv("data/cases_london by month.csv",
                          header = TRUE,
                          sep = ",",
                          encoding = "latin1")
```

This CSV file was downloaded from London Datastore. URL:https://data.london.gov.uk/download/coronavirus--covid-19--cases/151e497c-a16e-414e-9e03-9e428f555ae9/phe_cases_london_boroughs.csv 

The data have been processed by Excel. I create a PivotTable by selecting boroughs as rows. As for columns, I calculated the total number of cases monthly

Then I plot the bar charts of covid-19 to check their distributions.
```{r}
# selecting columns'month'
month<-factor(Covid_19_cases$month,levels=Covid_19_cases$month)
# After plotting, I find the x-axis placing in alphabetical order， rather than time series. So I use  'levels=Covid_19_cases$month' to make the order correctly.
number1_covid<-(Covid_19_cases$total_cases)/1000
# Resize the number of cases
df1<-data.frame(month,number1_covid)
library(ggplot2)
ggplot(df1,aes(month,number1_covid))+
  geom_bar(stat="identity",fill="steelblue")+
  # setting the labels
  labs(title = 'Total COVID-19 Cases in London by Month', x = 'month', y = 'monthly counts, London*1000' )+
  # adding the title
  theme(plot.title = element_text(size = 20,colour = "black",hjust = 0.5))
```

I also plotting the confirmed cases by boroughs
```{r}
Covid_cases<- read.csv("data/cases_london by boroughs.csv",
                          header = TRUE,
                          sep = ",",
                          encoding = "latin1")
#selecting the borough names and the confirmed number
boroughs_name1<-factor(Covid_cases$area_name,levels=Covid_cases$area_name)
number2_covid<-Covid_cases$total_cases
df2<-data.frame(number2_covid,boroughs_name1)
ggplot(df2,aes(number2_covid,boroughs_name1))+
  geom_bar(stat="identity",fill="steelblue")+
  labs(title = 'Total COVID-19 Cases by Boroughs up to 30/11/2020', x = 'number of cases', y = 'boroughs name' )+
  theme(plot.title = element_text(size = 20,colour = "black",hjust = 0.5))
```

I focuse on the accumulative value in last day

# Part 2: Loading the information about London boroughs

It is simple to read shapefile in R
```{r}
library(sf)
LondonBorough <- st_read(here::here("data",
                                    "statistical-gis-boundaries-london",
                                    "ESRI",
                                    "London_Borough_Excluding_MHW.shp"))
```

This CSV file was downloaded from London Datastore. URL:https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip

# Part 3: Load data of crime
```{r}
Crimes<- read.csv("data/MPS Ward Level Crime_edit.csv",
                  header = TRUE,
                  sep = ",",
                  encoding = "latin1")
```
This CSV file was downloaded from London Datastore.URL:https://data.london.gov.uk/download/recorded_crime_summary/d2e9ccfc-a054-41e3-89fb-53c2bc3ed87a/MPS%20Borough%20Level%20Crime%20%28most%20recent%2024%20months%29.csv

The data have been processed by Excel.I create a PivotTable by selecting boroughs as rows. As for columns, we just focus on ten major categories and record monthly. And I also create a new column called total cases which is the sum of offences in each borough.

# Part 4: Merging dataframe and connect to map
```{r}
#merge by common column
covid_crimes=merge(Covid_cases,Crimes,by.x="area_code",by.y="area_code")
# then put the covid_crime data into the map,  using the function of 'left_join' 
library(tidyverse)
LondonBoroughcases <- LondonBorough%>%
  left_join(.,
            covid_crimes,
            by = c("GSS_CODE" = "area_code"))
```

NOW, we can plot the map
```{r}
# checking the information about covid-19
g = ggplot(LondonBoroughcases) +
  # filled by the number of covid-19 cases
  geom_sf(aes(fill = total_cases)) +
  #choosing the patette of 'spectral'
  scale_fill_distiller("total_cases", palette = "Spectral") +
  ggtitle("covid_19_cases by boroughs")
g

#checking the information about crime
f = ggplot(LondonBoroughcases) +
  # filled by the number of crime cases
  geom_sf(aes(fill = Crime_cases)) +
  #choosing the patette of 'spectral'
  scale_fill_distiller("total_cases", palette = "Spectral") +
  ggtitle("Crime_cases by boroughs")
f
```

# Part 5: The structure breaks
```{r}
#loading data
Break_points<- read.csv("data/MPS Ward Level Crime_breakpoint.csv",
               header = TRUE,
               sep = ",",
               encoding = "latin1")
```

Converting Data on Energy Consumption to a Time Series Object
```{r}
# Define Arson and Criminal Damage (ACD) as a Time Series Object
ACD<-ts(Break_points$Arson.and.Criminal.Damage,frequency=12,start=c(2018,12))
#Define Burglary (B) as a Time Series Object
B<-ts(Break_points$Burglary,frequency=12,start=c(2018,12))
#Define Drug Offences (DO) as a Time Series Object
DO<-ts(Break_points$Drug.Offences,frequency=12,start=c(2018,12))
#Define Possession of Weapons (PW) as a Time Series Object
PW<-ts(Break_points$Possession.of.Weapons,frequency=12,start=c(2018,12))
#Define Robbery (R) as a Time Series Object
R<-ts(Break_points$Robbery,frequency=12,start=c(2018,12))
#Define Public Order Offences (POO) as a Time Series Object
POO<-ts(Break_points$Public.Order.Offences,frequency=12,start=c(2018,12))
#Define Sexual Offences (SO) as a Time Series Object
SO<-ts(Break_points$Sexual.Offences,frequency=12,start=c(2018,12))
#Define Theft (T) as a Time Series Object
T<-ts(Break_points$Theft,frequency=12,start=c(2018,12))
#Define Vehicle Offences (VO) as a Time Series Object
VO<-ts(Break_points$Vehicle.Offences,frequency=12,start=c(2018,12))
#Define Violence Against the Person (VAP) as a Time Series Object
VAP<-ts(Break_points$Violence.Against.the.Person,frequency=12,start=c(2018,12))
```

Plotting Data by Different Types of Crime
```{r}
#Plotting Data  by Different Types of Crime
plot(cbind(ACD, B, DO, PW, R, POO, SO, T, VO, VAP),
     main='Different Types of Crime in Time Series')
```

Identifying the breakpoints
```{r}
library(strucchange)
# Finding Structural Breaks in Arson and Criminal Damage (ACD)
ACD_bp<-breakpoints(ACD~1)
summary(ACD_bp)
# Plotting Structural Breaks in Arson and Criminal Damage (ACD)
ACD_ci <- confint(ACD_bp)
plot(ACD,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of ACD",col="blue")
lines(ACD_bp)
lines(ACD_ci)
```
```{r}
# Finding Structural Breaks in Burglary (B)
B_bp<-breakpoints(B~1)
summary(B_bp)
# Plotting Structural Breaks in Burglary (B)
B_ci <- confint(B_bp)
plot(B,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of B",col="blue")
lines(B_bp)
lines(B_ci)
```
```{r}
# Finding Structural in Drug Offences (DO) 
DO_bp<-breakpoints(DO~1)
summary(DO_bp)
# Plotting Structural Breaks in Drug Offences (DO) 
DO_ci <- confint(DO_bp)
plot(DO,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of DO",col="blue")
lines(DO_bp)
lines(DO_ci)
```
```{r}
# Finding Structural in Possession of Weapons (PW) 
PW_bp<-breakpoints(PW~1)
summary(PW_bp)
# Plotting Structural Breaks in Possession of Weapons (PW) 
PW_ci <- confint(PW_bp)
plot(PW,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of PW",col="blue")
lines(PW_bp)
lines(PW_ci)
```
```{r}
# Finding Structural in Robbery (R) 
R_bp<-breakpoints(R~1)
summary(R_bp)
# Plotting Structural Breaks in Robbery (R) 
R_ci <- confint(R_bp)
plot(R,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of R",col="blue")
lines(R_bp)
lines(R_ci)
```
```{r}
# Finding Structural in Public Order Offences (POO)
POO_bp<-breakpoints(POO~1)
summary(POO_bp)
# Plotting Structural Breaks in Public Order Offences (POO) 
POO_ci <- confint(POO_bp)
plot(POO,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of POO",col="blue")
lines(POO_bp)
lines(POO_ci)
```
```{r}
# Finding Structural in Sexual Offences (SO)
SO_bp<-breakpoints(SO~1)
summary(SO_bp)
# Plotting Structural Breaks in Sexual Offences (SO) 
SO_ci <- confint(SO_bp)
plot(SO,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of SO",col="blue")
lines(SO_bp)
lines(SO_ci)
```
```{r}
# Finding Structural in Theft (T) 
T_bp<-breakpoints(T~1)
summary(T_bp)
# Plotting Structural Breaks in Theft (T)  
T_ci <- confint(T_bp)
plot(T,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of T",col="blue")
lines(T_bp)
lines(T_ci)
```
```{r}
# Finding Structural in Vehicle Offences (VO) 
VO_bp<-breakpoints(VO~1)
summary(VO_bp)
# Plotting Structural Breaks in Vehicle Offences (VO)  
VO_ci <- confint(VO_bp)
plot(VO,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of VO",col="blue")
lines(VO_bp)
lines(VO_ci)
```
```{r}
# Finding Structural in Violence Against the Person (VAP)
VAP_bp<-breakpoints(VAP~1)
summary(VAP_bp)
# Plotting Structural Breaks in Violence Against the Person (VAP)  
VAP_ci <- confint(VAP_bp)
plot(VAP,type="l",las=1,xaxs="i",yaxs="i",xlab="time",ylab="total cases of VAP",col="blue")
lines(VAP_bp)
lines(VAP_ci)
```

# Part 6: The related changes
```{r}
#loading data
related_changes<- read.csv("data/MPS Ward Level Crime_related changes.csv",
                          header = TRUE,
                          sep = ",",
                          encoding = "latin1")
LondonBoroughcrimes <- LondonBorough%>%
  left_join(.,
            related_changes,
            by = c("NAME" = "boroughs_name"))
```
```{r}
# plotting the related changes on London boroughs
h = ggplot(LondonBoroughcrimes) +
  # selecting the crime of Drug Offences (DO)
  geom_sf(aes(fill = DO)) +
  # selecting the palette of 'PiYG'
  scale_fill_distiller("DO", palette = "PiYG") +
  ggtitle("the related change of Drug Offences by boroughs")
h
j = ggplot(LondonBoroughcrimes) +
  # selecting the crime of Burglary (B)
  geom_sf(aes(fill = B)) +
  # selecting the palette of 'PiYG'
  scale_fill_distiller("B", palette = "PiYG") +
  ggtitle("the related change of Burglary by boroughs")
j
```













